Test a simpler version of veb-boost performance mr.ash2s on ukbiobank data

### 2020-06-18 analysis/simulation-mr.ash2s-ukbchr22-gtex.adipose.Rmd
logging and more weights for chr22

We test the performance of mr.ash2s on ukbiobank data (chr22, n sample = 20,000). 
We use weights from Xiaotong, H3K27ac (trained using FUSION). Total features: > 8,000. on chromosome 22: 296.

@@

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200615/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200615/"
```

## Simulation 1
True parameters:
```{r para 1}
load(paste0(simdatadir, "simu_20200615-1-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200615-1.R"))
```

MR.ASH2s results (start from gene):
```{r sim 1 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200615-1-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200615-1"
simtag <- "20200615-1"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

MR.ASH results (start from SNP):
Very similar to start from gene, therefore, not shown.
```{r sim 1 snp, eval = F}
load(paste0(outputdir, "20200615-1-mr.ash2s.snp-res.Rd"))
g.fit <- mr.ash2s.fit$fit2
s.fit <-  mr.ash2s.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200615-1"
simtag <- "20200615-1"
plot_all(paste0(outputdir, tag, "-mr.ash2s.snp-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.snp-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 2}
load(paste0(simdatadir, "simu_20200615-2-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200615-2.R"))
```

MR.ASH results (start from gene):
```{r sim 2 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200615-2-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200615-2"
simtag <- "20200615-2"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 3}
load(paste0(simdatadir, "simu_20200615-3-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200615-3.R"))
```

MR.ASH results (start from gene):
```{r sim 3 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200615-3-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200615-3"
simtag <- "20200615-3"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 4}
load(paste0(simdatadir, "simu_20200615-4-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200615-4.R"))
```

MR.ASH results (start from gene):
```{r sim 4 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200615-4-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200615-4"
simtag <- "20200615-4"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

>>>>

We test the performance of mr.ash2s on ukbiobank data (chr22, n sample = 20,000). 
We use weights from Fusion website, using [Adipose (subcutaneous) p < 0.01](http://gusevlab.org/projects/fusion/weights/GTEx.Adipose_Subcutaneous.P01.tar.bz2).
Total features > 8,000. On chr22: 240.

@@

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
```

## Simulation 1
True parameters:
```{r para 1}
load(paste0(simdatadir, "simu_20200616-1-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-1.R"))
```

MR.ASH2s results (start from gene):
```{r sim 1 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-1-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-1"
simtag <- "20200616-1"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

MR.ASH results (start from SNP):
Very similar to start from gene, therefore, not shown.
```{r sim 1 snp, eval = F}
load(paste0(outputdir, "20200616-1-mr.ash2s.snp-res.Rd"))
g.fit <- mr.ash2s.fit$fit2
s.fit <-  mr.ash2s.fit$fit1
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-1"
simtag <- "20200616-1"
plot_all(paste0(outputdir, tag, "-mr.ash2s.snp-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.snp-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 2}
load(paste0(simdatadir, "simu_20200616-2-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-2.R"))
```

MR.ASH results (start from gene):
```{r sim 2 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-2-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-2"
simtag <- "20200616-2"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 3}
load(paste0(simdatadir, "simu_20200616-3-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-3.R"))
```

MR.ASH results (start from gene):
```{r sim 3 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-3-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-3"
simtag <- "20200616-3"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```

@@

True parameters:
```{r para 4}
load(paste0(simdatadir, "simu_20200616-4-pheno.Rd"))
readLines(paste0(simdatadir, "param-20200616-4.R"))
```

MR.ASH results (start from gene):
```{r sim 4 gene, out.width = "98%", out.height="95%"}
load(paste0(outputdir, "20200616-4-mr.ash2s.expr-res.Rd"))
g.fit <- mr.ash2s.fit$fit1
s.fit <-  mr.ash2s.fit$fit2
summary_mr.ash2(g.fit, s.fit, phenores)

tag <- "20200616-4"
simtag <- "20200616-4"
plot_all(paste0(outputdir, tag, "-mr.ash2s.expr-res.expr.txt"), paste0(simdatadir, simtag, ".exprgwas.txt.gz"), 
         paste0(outputdir, tag, "-mr.ash2s.expr-res.snp.txt"), paste0(simdatadir, simtag, ".snpgwas.txt.gz"))
```
